---
output: md_document
---

These are the libraries that needs to be installed before running any of the scripts.

```{r}
library(pomdpplus)
library(sarsop)
library(ggplot2)
library(dplyr)
library(tidyr)
source("../R/Fish_dynamic_Fun2.R")
source("../R/findpolicy_Milad2.R")
library(xml2)
library(MDPtoolbox)
source("../R/Interp_MM.R")
source("../R/L_fun.R")
library(nimble)
```

## Reading RAM data (No need because we have it saved)

```{r, eval=FALSE}
download.file("https://depts.washington.edu/ramlegac/wordpress/databaseVersions/RLSADB_v3.0_(assessment_data_only)_excel.zip",
              "ramlegacy.zip")
path <- unzip("ramlegacy.zip")
sheets <- readxl::excel_sheets(path)
ram <- lapply(sheets, readxl::read_excel, path = path)
names(ram) <- sheets


ram$timeseries_values_views %>%
  select(assessid, stockid, stocklong, year, SSB, TC) %>%
  left_join(ram$stock) %>%
  left_join(ram$area) %>%
  select(assessid, stockid, scientificname, commonname, areaname, country, year, SSB, TC) %>%
  left_join(ram$timeseries_units_views %>%
              rename(TC_units = TC, SSB_units = SSB)) %>%
  select(scientificname, commonname,  stockid, areaname, country, year, SSB, TC, SSB_units, TC_units) ->
  df

df2 <- df %>% filter(!is.na(df$SSB), !is.na(df$TC))
df2 <- df2 %>% filter(SSB_units == "MT", TC_units=="MT")
df2 <- df2 %>% filter(SSB > TC)

c = unique(df2$stockid)
data = vector("list",length = length(unique(df2$stockid)))
for(i in 1:length(data)){
  print(i)
  data[[i]]$commmonname = df2$commonname[df2$stockid == c[i]][1]
  data[[i]]$country = df2$country[df2$stockid == c[i]][1]
  data[[i]]$scientificname = df2$scientificname[df2$stockid == c[i]][1]
  data[[i]]$areaname = df2$areaname[df2$stockid == c[i]][1]
  data[[i]]$biomass = df2$SSB[df2$stockid == c[i]]
  data[[i]]$catch = df2$TC[df2$stockid == c[i]]
  data[[i]]$year = df2$year[df2$stockid == c[i]]
}

save(data, file = "../data/Rdata/RAM_data_us.RData")

```

## running Nimble

In this chunk we run NIMBLE to estimate the parameters of the population dynamics give the data. Again, the results are already saved under the data. 

```{r, eval=FALSE}
load("../data/RAM_data_us.RData")
est_bay <- vector("list",length = length(data))
scale = array(0, dim = length(data))
for(i in 1:length(data)){
  print(i)
  post = data[[i]]
  N = length(post$year)
  scale[i] = max(post$biomass)
  scaled_data <- data.frame(t = 1:N, y = post$biomass / scale[i], a = post$catch / scale[i])

  code <- nimbleCode({
         K ~ dunif(0, 1)
         r ~ dunif(0, 2)
     sigma ~ dunif(0, 0.5)

    x[1] <- x0
    for(t in 1:(N-1)){
      s[t] <-  x[t] - min(x[t], a[t])
      mu[t] <- s[t]  + r * s[t] *(1 - s[t] / K)
      x[t+1] ~ dnorm(mu[t], sd = sigma)
      }
  })


  constants <- list(N = N, a = scaled_data$a)
  inits <- list(K = 1, r = 0.1, sigma = 0.1, x0 = scaled_data$y[1])
  Rmodel <- nimbleModel(code = code, constants = constants, inits = inits, data = data.frame(x = scaled_data$y[1:N]))


 

  Cmodel <- compileNimble(Rmodel)
  Rmcmc <- buildMCMC(Rmodel)
  Cmcmc <- compileNimble(Rmcmc, project = Rmodel)
  Cmcmc$run(1e5)

  
  samples <- as.data.frame(as.matrix(Cmcmc$mvSamples))
  est_bay[[i]]$r = samples$r
  est_bay[[i]]$K = samples$K
  est_bay[[i]]$sigma = samples$sigma
}

#Saving this
#save(est_bay,file = "../data/Rdata/RAM_Nimble_estimates3.RData")

```

simplifying the estimation, this is done and the data is the data folder

```{r,eval=FALSE}


mean_r = array(0, dim = c(length(data)))
mean_K = array(0, dim = c(length(data)))
mean_G = array(0, dim = c(length(data)))
min_r = array(0, dim = c(length(data)))
max_r = array(0, dim = c(length(data)))
min_K = array(0, dim = c(length(data)))
max_K = array(0, dim = c(length(data)))
sd_r = array(0, dim = c(length(data)))
sd_K = array(0, dim = c(length(data)))

for(i in 1:length(data)){
  mean_r[i] = mean(est_bay[[i]]$r)
  mean_K[i] = mean(est_bay[[i]]$K)
  mean_G[i] = mean(est_bay[[i]]$sigma)
  min_r[i] = min(est_bay[[i]]$r)
  min_K[i] = min(est_bay[[i]]$K)
  max_r[i] = max(est_bay[[i]]$r)
  max_K[i] = max(est_bay[[i]]$K)
  sd_r[i] = sd(est_bay[[i]]$r)
  sd_K[i] = sd(est_bay[[i]]$K)
}

save(mean_r,mean_K,mean_G,min_r,min_K,max_r,max_K,sd_r,sd_K,file = "../data/Rdata/RAM_files3.RData")
```

