---
output: md_document
---

# Loading libraries 

```{r}

library(pomdpplus)
library(mdplearning)
library(sarsop)
library(ggplot2)
library(dplyr)
library(tidyr)
source("../R/Fish_dynamic_Fun2.R")
source("../R/fisheries_matrices.R")
source("../R/findpolicy_Milad2.R")
library(xml2)
library(MDPtoolbox)
source("../R/Interp_MM.R")
source("../R/L_fun.R")
```

# loading the policy files of POMDP runs
```{r}
# Loading the policy files of the pomdp runs
meta <- read.csv("../data/RAM4_large/meta.csv")
meta <- meta %>% arrange(Ind)

# loading the pre-estimated values of r, K and sigma_g that was estimated using Nimble
load("../data/RAM_files3.RData")

# truncating estimated sigma_gs larger than 0.2 to 0.2
mean_G[mean_G > 0.2] = 0.2


# defining state, observation and actions spaces
states = seq(0,2,by = 0.02)
actions <- states
obs <- states
# Initial probability over states
init = array(1, length(states))/ length(states)

### Loading alpha vectors and alpha actions (approximate value function of POMDP runs)
aa_ram = vector("list",length = dim(meta)[1])
av_ram = vector("list",length = dim(meta)[1])
Ind = meta$Ind
k = 1
for(i in 1:length(Ind)){
  id = as.character(meta$id[meta$Ind == Ind[i]])
  id_policy = paste0("../data/RAM4_large/",id,".policyx")
  out = findpolicy_Milad2(init, file = id_policy)
  av_ram[[k]] = out[[3]]
  aa_ram[[k]] = out[[4]] + 1
  k = k+1
}

# saving the results if needed
#save(av_ram,aa_ram,file = "RAM4_large_pomdp_model.RData")
```


# creating transition, emission and rewards functions for each stock
```{r}

Ind = meta$Ind
y = vector("list", length = length(Ind))
a = vector("list", length = length(Ind))
TT = vector("list", length = length(Ind))
TTT = vector("list", length = length(Ind))
OO = vector("list", length = length(Ind))
R = vector("list", length = length(Ind))


GAMMA = 0.99

# this is the large measurement noise (for small and medium this should be changed to 0.1 and 0.05)
sigma_m = 0.2

for(ii in 1:length(Ind)){
  cc <- fisheries_matrices(states,actions,obs,f = logistic, sigma_g = mean_G[ii],
                           sigma_m = sigma_m, r = mean_r[ii],K = mean_K[ii], noise = "normal")
  TT[[ii]] = cc$transition
  OO[[ii]] = cc$observation
  R[[ii]] = cc$reward
}

#save(TT,OO,R, file = "RAM4_large_model.RDAta")
```


# deterministic policy

```{r}
load("../data/RAM_data_us.RData")
det_aa_ram = vector("list", length = length(data))
det_av_ram = vector("list", length = length(data))

f <- function(x, h,r,K){
  s <- pmax(x - h, 0)
  s + s * r * (1 - s / K) 
} 

for(i in 1:length(data)){
  S_star <- optimize(function(x) x / GAMMA - f(x,0,mean_r[i],mean_K[i]), c(min(states),max(states)))$minimum
  det <- pmax(states - S_star, 0)
  for(j in 1:length(actions)){
    det_aa_ram[[i]][j] = which.min(abs(actions-det[j]))
  }
}
#save(det_av_ram,det_aa_ram,file = "RAM4_large_mdp2.RData")
```

# reading the trajectories of stocks and normalizing them based on states and actions

```{r}
load("../data/RAM_data_us.RData")
N = array(0, dim = length(Ind))
y = vector("list", length = length(Ind))
a = vector("list", length = length(Ind))
scale = array(0, dim = length(Ind))
name = character(length = length(Ind))
for(ii in 1:length(Ind)){
  post <- data[[ii]]
  name[ii] = post$commmonname
  N[ii] <- length(post$year)
  scale[ii] <- max(post$biomass)
  scaled_data <- data.frame(t = 1:N[ii], y = post$biomass / scale[ii], 
                            a = post$catch / scale[ii])
  y[[ii]] <- sapply(scaled_data$y, function(y) which.min(abs(states - y)))
  a[[ii]] <- sapply(scaled_data$a, function(a) which.min(abs(actions - a)))
}

```

# forward projections of POMDP

```{r, cache = TRUE, eval= FALSE}

## Need to run this for different sigma_ms with different models created in the above chunks and save the results accordingly


pomdp_proj_st = vector("list", length = length(Ind))
pomdp_proj_act = vector("list", length = length(Ind))
pomdp_proj_obs = vector("list", length = length(Ind))
pomdp_proj_rew = vector("list", length = length(Ind))

# Number of time steps for projections and number of simulations
Tmax = 100; Num_sim = 100
for(i in 1:length(Ind)){
  yy = y[[i]]
  aa= a[[i]]
  nn = N[i]
  
  
  pomdp_proj_st[[i]] = array(0, dim = c(Num_sim,Tmax))
  pomdp_proj_obs[[i]] = array(0, dim = c(Num_sim,Tmax))
  pomdp_proj_rew[[i]] = array(0, dim = c(Num_sim,Tmax))
  pomdp_proj_act[[i]] = array(0, dim = c(Num_sim,Tmax))
  
  for(m in 1:Num_sim){
    
    pomdp_proj_st[[i]][m,1] = yy[nn]
    b = array(0, dim = length(states)); b[pomdp_proj_st[[i]][m,1]] = 1
    
    uu <- Interp_MM(b,av_ram[[i]],aa_ram[[i]])
    pomdp_proj_act[[i]][m,1] = uu[[2]]
    for(j in 1:(Tmax-1)){
      out <- fakemodel(TT[[i]],OO[[i]],pomdp_proj_st[[i]][m,j],pomdp_proj_act[[i]][m,j],R[[i]],length(states),length(obs))
      pomdp_proj_st[[i]][m,j+1] = out[[1]]
      pomdp_proj_obs[[i]][m,j] = out[[2]]
      pomdp_proj_rew[[i]][m,j] = out[[3]]
      b = update_belief(b,TT[[i]],OO[[i]],pomdp_proj_act[[i]][m,j],pomdp_proj_obs[[i]][m,j])
      uu <- Interp_MM(b,av_ram[[i]],aa_ram[[i]])
      pomdp_proj_act[[i]][m,j+1] = uu[[2]]
    }
  }
}

#save(pomdp_proj_act,pomdp_proj_obs,pomdp_proj_rew,pomdp_proj_st, file = "RAM4_large_pomdp_proj.RData")


```

# forward projections of deterministic case

```{r, cache = TRUE, eval=FALSE}

## Need to run this for different sigma_ms with different models created in the above chunks and save the results accordingly

mdp_aa_ram = det_aa_ram; mdp_av_ram = det_av_ram
mdp_proj_st = vector("list", length = length(data))
mdp_proj_act = vector("list", length = length(data))
mdp_proj_rew = vector("list", length = length(data))

Tmax = 100; Num_sim = 100
for(i in 1:length(data)){
  n = i
  yy = y[[n]]
  aa= a[[n]]
  nn = N[n]
  
  mdp_proj_st[[i]] = array(0, dim = c(Num_sim,Tmax))
  mdp_proj_act[[i]] = array(0, dim = c(Num_sim,Tmax))
  mdp_proj_rew[[i]] = array(0, dim = c(Num_sim,Tmax))
  
  for(m in 1:Num_sim){
    mdp_proj_st[[i]][m,1] = yy[nn]
    mdp_proj_act[[i]][m,1] = mdp_aa_ram[[i]][mdp_proj_st[[i]][m,1]]
    output <- mdp_planning(transition = TT[[i]],reward = R[[i]],discount = GAMMA,x0 = yy[nn],Tmax = Tmax,observation = OO[[i]],policy = mdp_aa_ram[[i]])
    mdp_proj_st[[i]][m,] = output$state#stateee[time]#output$state
    mdp_proj_act[[i]][m,] = output$action#actionnn[time]#output$action
    for(jj in 1:length(mdp_proj_st[[i]][m,])){
      mdp_proj_rew[[i]][m,jj] = R[[i]][mdp_proj_st[[i]][m,jj],mdp_proj_act[[i]][m,jj]]
    }
    
  }
}

#save(mdp_proj_act,mdp_proj_rew,mdp_proj_st, file = "RAM4_zero_MDP_proj.RData")

```

# MSY projections

```{r, cache = TRUE,eval=FALSE}

## Need to run this for different sigma_ms with different models created in the above chunks and save the results accordingly

msy_proj_st = vector("list", length = length(av_ram))
msy_proj_act = vector("list", length = length(av_ram))
msy_proj_rew = vector("list", length = length(av_ram))

Tmax = 100; Num_sim = 100
for(i in 1:length(av_ram)){
  n = i
  yy = y[[n]]
  aa= a[[n]]
  nn = N[n]
  msy_proj_st[[i]] = array(0, dim = c(Num_sim,Tmax))
  msy_proj_act[[i]] = array(0, dim = c(Num_sim,Tmax))
  msy_proj_rew[[i]] = array(0, dim = c(Num_sim,Tmax))
  
  
  S_star = mean_K[i]/2
  B_MSY <- f(S_star,0,mean_r[i],mean_K[i])
  H_MSY <- f(S_star,0,mean_r[i],mean_K[i]) - S_star 
  F_MSY <- H_MSY / B_MSY
  F_PGY = F_MSY
  for(m in 1:Num_sim){
    msy_proj_st[[i]][m,1] = yy[nn]
    x = F_PGY * states[msy_proj_st[[i]][m,1]]
    msy_proj_act[[i]][m,1] = which.min(abs(actions - x))
    xx = array(0, dim = length(states))
    for(jjj in 1:length(xx)){
      x = F_PGY * states[jjj]
      xx[jjj] = which.min(abs(actions - x))
    }
    output <- mdp_planning(transition = TT[[i]],reward = R[[i]],discount = GAMMA,x0 = yy[nn],Tmax = Tmax,observation = OO[[i]],policy = xx)
    msy_proj_st[[i]][m,] = output$state
    msy_proj_act[[i]][m,] = output$action
    for(jj in 1:length(msy_proj_st[[i]][m,])){
      msy_proj_rew[[i]][m,jj] = R[[i]][msy_proj_st[[i]][m,jj],msy_proj_act[[i]][m,jj]]
    }
  }
}


#save(msy_proj_act,msy_proj_rew,msy_proj_st, file = "RAM4_zero_MSY_real_proj.RData")


```

# Filling the data for each small, medium and large scenarios

```{r}
load("../data/RAM4_small_pomdp_proj.RData")
load("../data/RAM4_small_MSY_real_proj.RData")
load("../data/RAM4_small_MDP_proj.RData")

indddd = c()

pomdp_proj_st2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_rew2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_st2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_rew2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_st2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_rew2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_act2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_act2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_act2_s = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
Ind_new_s = array(0, dim = (length(pomdp_proj_st)-length(indddd)))

k = 1
for(i in 1:length(Ind)){
  if(sum(indddd == Ind[i]) == 0){
    pomdp_proj_st2_s[[k]] = pomdp_proj_st[[i]]
    pomdp_proj_rew2_s[[k]] = pomdp_proj_rew[[i]]
    mdp_proj_st2_s[[k]] = mdp_proj_st[[i]]
    mdp_proj_rew2_s[[k]] = mdp_proj_rew[[i]]
    det_8_proj_st2_s[[k]] = msy_proj_st[[i]]
    det_8_proj_rew2_s[[k]] = msy_proj_rew[[i]]
    pomdp_proj_act2_s[[k]] = pomdp_proj_act[[i]]
    mdp_proj_act2_s[[k]] = mdp_proj_act[[i]]
    det_8_proj_act2_s[[k]] = msy_proj_act[[i]]
    Ind_new_s[k] = Ind[i]
    k = k + 1
  }
}


load("../data/RAM4_large_pomdp_proj.RData")
load("../data/RAM4_large_MSY_real_proj.RData")
load("../data/RAM4_large_MDP_proj.RData")

pomdp_proj_st2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_rew2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_st2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_rew2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_st2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_rew2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_act2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_act2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_act2_l = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
Ind_new_l = array(0, dim = (length(pomdp_proj_st)-length(indddd)))

k = 1
for(i in 1:length(Ind)){
  if(sum(indddd == Ind[i]) == 0){
    pomdp_proj_st2_l[[k]] = pomdp_proj_st[[i]]
    pomdp_proj_rew2_l[[k]] = pomdp_proj_rew[[i]]
    mdp_proj_st2_l[[k]] = mdp_proj_st[[i]]
    mdp_proj_rew2_l[[k]] = mdp_proj_rew[[i]]
    det_8_proj_st2_l[[k]] = msy_proj_st[[i]]
    det_8_proj_rew2_l[[k]] = msy_proj_rew[[i]]
    pomdp_proj_act2_l[[k]] = pomdp_proj_act[[i]]
    mdp_proj_act2_l[[k]] = mdp_proj_act[[i]]
    det_8_proj_act2_l[[k]] = msy_proj_act[[i]]
    Ind_new_l[k] = Ind[i]
    k = k + 1
  }
}




load("../data/RAM4_medium_pomdp_proj.RData")
load("../data/RAM4_medium_MSY_real_proj.RData")
load("../data/RAM4_medium_MDP_proj.RData")

pomdp_proj_st2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_rew2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_st2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_rew2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_st2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_rew2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_act2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_act2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_act2_medh = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
Ind_new_medh = array(0, dim = (length(pomdp_proj_st)-length(indddd)))

k = 1
for(i in 1:length(Ind)){
  if(sum(indddd == Ind[i]) == 0){
    pomdp_proj_st2_medh[[k]] = pomdp_proj_st[[i]]
    pomdp_proj_rew2_medh[[k]] = pomdp_proj_rew[[i]]
    mdp_proj_st2_medh[[k]] = mdp_proj_st[[i]]
    mdp_proj_rew2_medh[[k]] = mdp_proj_rew[[i]]
    det_8_proj_st2_medh[[k]] = msy_proj_st[[i]]
    det_8_proj_rew2_medh[[k]] = msy_proj_rew[[i]]
    pomdp_proj_act2_medh[[k]] = pomdp_proj_act[[i]]
    mdp_proj_act2_medh[[k]] = mdp_proj_act[[i]]
    det_8_proj_act2_medh[[k]] = msy_proj_act[[i]]
    Ind_new_medh[k] = Ind[i]
    k = k + 1
  }
}





load("../data/RAM4_zero_MSY_real_proj.RData")
load("../data/RAM4_zero_MDP_proj.RData")

pomdp_proj_st2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_rew2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_st2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_rew2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_st2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_rew2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
pomdp_proj_act2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
mdp_proj_act2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
det_8_proj_act2_medl = vector("list", length =(length(pomdp_proj_st)-length(indddd)))
Ind_new_medl = array(0, dim = (length(pomdp_proj_st)-length(indddd)))

k = 1
for(i in 1:length(Ind)){
  if(sum(indddd == Ind[i]) == 0){
    pomdp_proj_st2_medl[[k]] = mdp_proj_st[[i]]
    pomdp_proj_rew2_medl[[k]] = mdp_proj_rew[[i]]
    mdp_proj_st2_medl[[k]] = mdp_proj_st[[i]]
    mdp_proj_rew2_medl[[k]] = mdp_proj_rew[[i]]
    det_8_proj_st2_medl[[k]] = msy_proj_st[[i]]
    det_8_proj_rew2_medl[[k]] = msy_proj_rew[[i]]
    pomdp_proj_act2_medl[[k]] = mdp_proj_act[[i]]
    mdp_proj_act2_medl[[k]] = mdp_proj_act[[i]]
    det_8_proj_act2_medl[[k]] = msy_proj_act[[i]]
    Ind_new_medl[k] = Ind[i]
    k = k + 1
  }
}




## calculating the percentage above 80% B_MSY

pomdp_proj_st_l = vector("list", length = length(pomdp_proj_st2_l))
mdp_proj_st_l = vector("list", length = length(pomdp_proj_st2_l))
det_8_proj_st_l = vector("list", length = length(pomdp_proj_st2_l))
pomdp_proj_st_s = vector("list", length = length(pomdp_proj_st2_l))
mdp_proj_st_s = vector("list", length = length(pomdp_proj_st2_l))
det_8_proj_st_s = vector("list", length = length(pomdp_proj_st2_l))
pomdp_proj_st_medh = vector("list", length = length(pomdp_proj_st2_l))
mdp_proj_st_medh = vector("list", length = length(pomdp_proj_st2_l))
det_8_proj_st_medh = vector("list", length = length(pomdp_proj_st2_l))


for(i in 1:length(pomdp_proj_st2_l)){
  k = i
  pomdp_proj_st_l[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  mdp_proj_st_l[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  det_8_proj_st_l[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  pomdp_proj_st_s[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  mdp_proj_st_s[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  det_8_proj_st_s[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  pomdp_proj_st_medh[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  mdp_proj_st_medh[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  det_8_proj_st_medh[[k]] = array(0, dim = dim(pomdp_proj_st2_l[[i]]))
  
  for(j in 1:dim(pomdp_proj_st2_l[[i]])[1]){
    pomdp_proj_st_l[[k]][j,] = states[pomdp_proj_st2_l[[i]][j,]]
    mdp_proj_st_l[[k]][j,] = states[mdp_proj_st2_l[[i]][j,]]
    det_8_proj_st_l[[k]][j,] = states[det_8_proj_st2_l[[i]][j,]]
    
    pomdp_proj_st_s[[k]][j,] = states[pomdp_proj_st2_s[[i]][j,]]
    mdp_proj_st_s[[k]][j,] = states[mdp_proj_st2_s[[i]][j,]]
    det_8_proj_st_s[[k]][j,] = states[det_8_proj_st2_s[[i]][j,]]
    
    pomdp_proj_st_medh[[k]][j,] = states[pomdp_proj_st2_medh[[i]][j,]]
    mdp_proj_st_medh[[k]][j,] = states[mdp_proj_st2_medh[[i]][j,]]
    det_8_proj_st_medh[[k]][j,] = states[det_8_proj_st2_medh[[i]][j,]]
    
  }
}


bb_pomdp_large = vector("list", length = length(pomdp_proj_st2_l))
bb_pomdp_small = vector("list", length = length(pomdp_proj_st2_l))
bb_pomdp_medh = vector("list", length = length(pomdp_proj_st2_l))
bb_mdp_large = vector("list", length = length(pomdp_proj_st2_l))
bb_mdp_small = vector("list", length = length(pomdp_proj_st2_l))
bb_mdp_medh = vector("list", length = length(pomdp_proj_st2_l))
bb_msy_large = vector("list", length = length(pomdp_proj_st2_l))
bb_msy_small = vector("list", length = length(pomdp_proj_st2_l))
bb_msy_medh = vector("list", length = length(pomdp_proj_st2_l))


k=1
for(i in 1:length(pomdp_proj_st2_l)){
  k = i  
  n = Ind_new_l[i]
  S_star = mean_K[n]/2
  B_MSY <- f(S_star,0,mean_r[n],mean_K[n])
  H_MSY <- f(S_star,0,mean_r[n],mean_K[n]) - S_star 
  F_MSY <- H_MSY / B_MSY
  F_PGY = F_MSY
  bb_pomdp_large[[k]] = pomdp_proj_st_l[[k]] / B_MSY
  bb_pomdp_small[[k]] = pomdp_proj_st_s[[k]] / B_MSY
  bb_pomdp_medh[[k]] = pomdp_proj_st_medh[[k]] / B_MSY
  bb_mdp_large[[k]] = mdp_proj_st_l[[k]] / B_MSY
  bb_mdp_small[[k]] = mdp_proj_st_s[[k]] / B_MSY
  bb_mdp_medh[[k]] = mdp_proj_st_medh[[k]] / B_MSY
  bb_msy_large[[k]] = det_8_proj_st_l[[k]] / B_MSY
  bb_msy_small[[k]] = det_8_proj_st_s[[k]] / B_MSY
  bb_msy_medh[[k]] = det_8_proj_st_medh[[k]] / B_MSY
  
}


ind_pomdp_large = vector("list", length = length(pomdp_proj_st_l))
ind_pomdp_small = vector("list", length = length(pomdp_proj_st_l))
ind_pomdp_medh = vector("list", length = length(pomdp_proj_st_l))
ind_mdp_large = vector("list", length = length(pomdp_proj_st_l))
ind_mdp_small = vector("list", length = length(pomdp_proj_st_l))
ind_mdp_medh = vector("list", length = length(pomdp_proj_st_l))
ind_msy_large = vector("list", length = length(pomdp_proj_st_l))
ind_msy_small = vector("list", length = length(pomdp_proj_st_l))
ind_msy_medh = vector("list", length = length(pomdp_proj_st_l))

for(i in 1:length(bb_pomdp_large)){
  ind_pomdp_large[[i]] = bb_pomdp_large[[i]] >= 0.8
  ind_pomdp_small[[i]] = bb_pomdp_small[[i]] >= 0.8
  ind_pomdp_medh[[i]] = bb_pomdp_medh[[i]] >= 0.8
  
  ind_mdp_large[[i]] = bb_mdp_large[[i]] >= 0.8
  ind_mdp_small[[i]] = bb_mdp_small[[i]] >= 0.8
  ind_mdp_medh[[i]] = bb_mdp_medh[[i]] >= 0.8
  
  ind_msy_large[[i]] = bb_msy_large[[i]] >= 0.8
  ind_msy_small[[i]] = bb_msy_small[[i]] >= 0.8
  ind_msy_medh[[i]] = bb_msy_medh[[i]] >= 0.8
}

find_pomdp_large = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_pomdp_small = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_pomdp_medh = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_mdp_large = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_mdp_small = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_mdp_medh = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_msy_large = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_msy_small = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))
find_msy_medh = array(0, dim = c(length(pomdp_proj_st_l), 100, 100))

for(i in 1:length(pomdp_proj_st_l)){
  find_pomdp_large[i,,] = ind_pomdp_large[[i]]
  find_pomdp_small[i,,] = ind_pomdp_small[[i]]
  find_pomdp_medh[i,,] = ind_pomdp_medh[[i]]
  find_mdp_large[i,,] = ind_mdp_large[[i]]
  find_mdp_small[i,,] = ind_mdp_small[[i]]
  find_mdp_medh[i,,] = ind_mdp_medh[[i]]
  find_msy_large[i,,] = ind_msy_large[[i]]
  find_msy_small[i,,] = ind_msy_small[[i]]
  find_msy_medh[i,,] = ind_msy_medh[[i]]
}



ff_pomdp_large = apply(find_pomdp_large,c(2,3),mean)
ff_pomdp_small = apply(find_pomdp_small,c(2,3),mean)
ff_pomdp_medh = apply(find_pomdp_medh,c(2,3),mean)
ff_mdp_large = apply(find_mdp_large,c(2,3),mean)
ff_mdp_small = apply(find_mdp_small,c(2,3),mean)
ff_mdp_medh = apply(find_mdp_medh,c(2,3),mean)
ff_msy_large = apply(find_msy_large,c(2,3),mean)
ff_msy_small = apply(find_msy_small,c(2,3),mean)
ff_msy_medh = apply(find_msy_medh,c(2,3),mean)


## finding the same for historical data that have data between  1980 and 2007
low = 1980; high = 2007
max_year = array(0, dim = length(data))
min_year = array(0, dim = length(data))

for(i in 1:length(data)){
  post = data[[i]]
  max_year[i] = max(post$year)
  min_year[i] = min(post$year)
}
ind = array(0, dim = length(pomdp_proj_st2_l))
for(i in 1:length(pomdp_proj_st2_l)){
  if(min_year[Ind_new_l[i]] <= low && max_year[Ind_new_l[i]] >= high){
    ind[i] = 1
  }
}
find_biomass = array(0, dim = c(sum(ind), 28))
find_biomass2 = array(0, dim = c(sum(ind), 28))

k = 1
for(i in 1:length(Ind)){
  if(ind[i] == 1){
    n = i
    post = data[[n]]
    year = post$year
    nom = post$year[post$year %in% seq(low,high)] - (low-1)
    find_biomass[k,nom] = (post$biomass[post$year %in% seq(low,high)] / scale[n]) / (mean_K[n]/2) * 100
    find_biomass2[k,nom] = (post$biomass[post$year %in% seq(low,high)] / scale[n]) / (mean_K[n]) * 100
    k = k+1
  }
}


cc = apply(find_biomass == 0, 2,sum)
ind_biomass = find_biomass >= 80
ff_biomass = array(0, dim = dim(find_biomass)[2])
for(i in 1:dim(find_biomass)[2]){
  ff_biomass[i] = sum(ind_biomass[,i]) / (dim(find_biomass)[1] - cc[i]) 
}



```


```{r}

years = seq(low,high)
Tmax = 100; Num_sim = 100
t = c(years,seq(years[length(years)]+1,(years[length(years)]+ Tmax-1)))
model = c("SDP","ORM", "History","MSY")
type = c("5% Error","10% Error","20% Error")
qqq = expand.grid(t,1:Num_sim, model,type)
traj = array(0, dim = dim(qqq)[1])

biomass_pomdp_l = array(0,dim = c(Num_sim,length(t)))
biomass_pomdp_s = array(0,dim = c(Num_sim,length(t)))
biomass_pomdp_medh = array(0,dim = c(Num_sim,length(t)))

biomass_mdp_l = array(0,dim = c(Num_sim,length(t)))
biomass_mdp_s = array(0,dim = c(Num_sim,length(t)))
biomass_mdp_medh = array(0,dim = c(Num_sim,length(t)))

biomass_MSY_l = array(0,dim = c(Num_sim,length(t)))
biomass_MSY_s = array(0,dim = c(Num_sim,length(t)))
biomass_MSY_medh = array(0,dim = c(Num_sim,length(t)))

biomass = array(0,dim = c(Num_sim,length(t)))
for(j in 1:Num_sim){
  biomass[j,1:28] = ff_biomass * 100
}


mm = length(low:high)+1; nn = length(low:high)+99 
biomass_pomdp_l[,(mm:nn)] = ff_pomdp_large[,1:99] * 100
biomass_pomdp_s[,(mm:nn)] = ff_pomdp_small[,1:99] * 100
biomass_pomdp_medh[,(mm:nn)] = ff_pomdp_medh[,1:99] * 100

biomass_mdp_l[,(mm:nn)] = ff_mdp_large[,1:99] * 100
biomass_mdp_s[,(mm:nn)] = ff_mdp_small[,1:99] * 100
biomass_mdp_medh[,(mm:nn)] = ff_mdp_medh[,1:99] * 100

biomass_MSY_l[,(mm:nn)] = ff_msy_large[,1:99] * 100
biomass_MSY_s[,(mm:nn)] = ff_msy_small[,1:99] * 100
biomass_MSY_medh[,(mm:nn)] = ff_msy_medh[,1:99] * 100


biomass_pomdp_l[,length(low:high)] = biomass[,length(low:high)]
biomass_mdp_l[,length(low:high)] = biomass[,length(low:high)]
biomass_pomdp_medh[,length(low:high)] = biomass[,length(low:high)]
biomass_mdp_medh[,length(low:high)] = biomass[,length(low:high)]
biomass_MSY_l[,length(low:high)] = biomass[,length(low:high)]
biomass_MSY_medh[,length(low:high)] = biomass[,length(low:high)]
biomass_pomdp_s[,length(low:high)] = biomass[,length(low:high)]
biomass_mdp_s[,length(low:high)] = biomass[,length(low:high)]
biomass_MSY_s[,length(low:high)] = biomass[,length(low:high)]


for(i in 1:Num_sim){
  traj[(qqq$Var2 == i & qqq$Var3 == "History")] = biomass[i,]
  
  traj[(qqq$Var2 == i & qqq$Var3 == "ORM" & qqq$Var4 == "20% Error")] = biomass_pomdp_l[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "ORM" & qqq$Var4 == "5% Error")] = biomass_pomdp_s[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "ORM" & qqq$Var4 == "10% Error")] = biomass_pomdp_medh[i,]
  
  traj[(qqq$Var2 == i & qqq$Var3 == "SDP" & qqq$Var4 == "20% Error")] = biomass_mdp_l[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "SDP" & qqq$Var4 == "5% Error")] = biomass_mdp_s[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "SDP" & qqq$Var4 == "10% Error")] = biomass_mdp_medh[i,]
  
  traj[(qqq$Var2 == i & qqq$Var3 == "MSY" & qqq$Var4 == "20% Error")] = biomass_MSY_l[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "MSY" & qqq$Var4 == "5% Error")] = biomass_MSY_s[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "MSY" & qqq$Var4 == "10% Error")] = biomass_MSY_medh[i,]
}

qqq = data.frame(qqq,traj)

qqq$traj[qqq$Var3 == "History" &  qqq$Var1 %in% seq((high+1),(high+99))] = NA
qqq$traj[qqq$Var3 == "ORM" &  qqq$Var1 %in% seq(low,(high-1))] = NA
qqq$traj[qqq$Var3 == "SDP" &  qqq$Var1 %in% seq(low,(high-1))] = NA
qqq$traj[qqq$Var3 == "MSY" &  qqq$Var1 %in% seq(low,(high-1))] = NA


font = 22
qqq %>% filter(Var1 <= 2050) %>% ggplot(aes(Var1, traj)) +
  stat_summary(aes(color = Var3), geom = "line", fun.y = mean, lwd = 1) + 
  stat_summary(aes(fill = Var3), geom = "ribbon", fun.data = mean_sdl, fun.args = list(mult = 2), alpha = .2) +
  theme_bw() + ylab(expression(paste("% of stock above 80% ", B, "/", B[MSY]))) + xlab("Year")  + 
  facet_wrap(~Var4, nrow = 2, strip.position = "top") +
  scale_color_manual(values = c("goldenrod1","#00BFC4","blueviolet","#F8766D")) + 
  scale_fill_manual(values = c("goldenrod1","#00BFC4","blueviolet","#F8766D")) + 
  theme(legend.title=element_blank(), axis.title.x = element_text(size = font), 
        axis.title.y = element_text(size = font), legend.text = element_text(size = font) ,
        legend.position = "top",axis.text = element_text(size = font), strip.text = element_text(size = font),
        plot.margin=unit(c(1,1,0.5,0.5),"cm")) + coord_fixed(ylim = c(0,100), ratio = 0.56)

```

# Visualization

```{r}
low = 1980; high = 2007
max_year = array(0, dim = length(data))
min_year = array(0, dim = length(data))

for(i in 1:length(data)){
  post = data[[i]]
  max_year[i] = max(post$year)
  min_year[i] = min(post$year)
}
ind = array(0, dim = length(pomdp_proj_st2_l))
for(i in 1:length(pomdp_proj_st2_l)){
  if(min_year[Ind_new_l[i]] <= low && max_year[Ind_new_l[i]] >= high){
    ind[i] = 1
  }
}

years = seq(low,high)
Tmax = 100; Num_sim = 100
t = c(years,seq(years[length(years)]+1,(years[length(years)]+ Tmax-1)))
model = c("SDP","ORM", "History","MSY")
type = c("5% Error","10% Error","20% Error")
qqq = expand.grid(t,1:Num_sim, model,type)
traj = array(0, dim = dim(qqq)[1])

biomass_pomdp_l = array(0,dim = c(Num_sim,length(t)))
biomass_pomdp_s = array(0,dim = c(Num_sim,length(t)))
biomass_pomdp_medh = array(0,dim = c(Num_sim,length(t)))

biomass_mdp_l = array(0,dim = c(Num_sim,length(t)))
biomass_mdp_s = array(0,dim = c(Num_sim,length(t)))
biomass_mdp_medh = array(0,dim = c(Num_sim,length(t)))

biomass_MSY_l = array(0,dim = c(Num_sim,length(t)))
biomass_MSY_s = array(0,dim = c(Num_sim,length(t)))
biomass_MSY_medh = array(0,dim = c(Num_sim,length(t)))

biomass = array(0,dim = c(Num_sim,length(t)))
for(j in 1:Num_sim){
  biomass[j,1:28] = ff_biomass * 100
}


    mm = length(low:high)+1; nn = length(low:high)+99 
    biomass_pomdp_l[,(mm:nn)] = ff_pomdp_large[,1:99] * 100
    biomass_pomdp_s[,(mm:nn)] = ff_pomdp_small[,1:99] * 100
    biomass_pomdp_medh[,(mm:nn)] = ff_pomdp_medh[,1:99] * 100

    biomass_mdp_l[,(mm:nn)] = ff_mdp_large[,1:99] * 100
    biomass_mdp_s[,(mm:nn)] = ff_mdp_small[,1:99] * 100
    biomass_mdp_medh[,(mm:nn)] = ff_mdp_medh[,1:99] * 100

    biomass_MSY_l[,(mm:nn)] = ff_msy_large[,1:99] * 100
    biomass_MSY_s[,(mm:nn)] = ff_msy_small[,1:99] * 100
    biomass_MSY_medh[,(mm:nn)] = ff_msy_medh[,1:99] * 100


biomass_pomdp_l[,length(low:high)] = biomass[,length(low:high)]
biomass_mdp_l[,length(low:high)] = biomass[,length(low:high)]
biomass_pomdp_medh[,length(low:high)] = biomass[,length(low:high)]
biomass_mdp_medh[,length(low:high)] = biomass[,length(low:high)]
biomass_MSY_l[,length(low:high)] = biomass[,length(low:high)]
biomass_MSY_medh[,length(low:high)] = biomass[,length(low:high)]
biomass_pomdp_s[,length(low:high)] = biomass[,length(low:high)]
biomass_mdp_s[,length(low:high)] = biomass[,length(low:high)]
biomass_MSY_s[,length(low:high)] = biomass[,length(low:high)]


for(i in 1:Num_sim){
  traj[(qqq$Var2 == i & qqq$Var3 == "History")] = biomass[i,]

  traj[(qqq$Var2 == i & qqq$Var3 == "ORM" & qqq$Var4 == "20% Error")] = biomass_pomdp_l[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "ORM" & qqq$Var4 == "5% Error")] = biomass_pomdp_s[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "ORM" & qqq$Var4 == "10% Error")] = biomass_pomdp_medh[i,]

  traj[(qqq$Var2 == i & qqq$Var3 == "SDP" & qqq$Var4 == "20% Error")] = biomass_mdp_l[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "SDP" & qqq$Var4 == "5% Error")] = biomass_mdp_s[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "SDP" & qqq$Var4 == "10% Error")] = biomass_mdp_medh[i,]

  traj[(qqq$Var2 == i & qqq$Var3 == "MSY" & qqq$Var4 == "20% Error")] = biomass_MSY_l[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "MSY" & qqq$Var4 == "5% Error")] = biomass_MSY_s[i,]
  traj[(qqq$Var2 == i & qqq$Var3 == "MSY" & qqq$Var4 == "10% Error")] = biomass_MSY_medh[i,]
}

qqq = data.frame(qqq,traj)

qqq$traj[qqq$Var3 == "History" &  qqq$Var1 %in% seq((high+1),(high+99))] = NA
qqq$traj[qqq$Var3 == "ORM" &  qqq$Var1 %in% seq(low,(high-1))] = NA
qqq$traj[qqq$Var3 == "SDP" &  qqq$Var1 %in% seq(low,(high-1))] = NA
qqq$traj[qqq$Var3 == "MSY" &  qqq$Var1 %in% seq(low,(high-1))] = NA


font = 22
qqq %>% filter(Var1 <= 2050) %>% ggplot(aes(Var1, traj)) +
  stat_summary(aes(color = Var3), geom = "line", fun.y = mean, lwd = 1) + 
  stat_summary(aes(fill = Var3), geom = "ribbon", fun.data = mean_sdl, fun.args = list(mult = 2), alpha = .2) +
  theme_bw() + ylab(expression(paste("% of stock above 80% ", B, "/", B[MSY]))) + xlab("Year")  + 
  facet_wrap(~Var4, nrow = 2, strip.position = "top") +
  scale_color_manual(values = c("goldenrod1","#00BFC4","blueviolet","#F8766D")) + 
  scale_fill_manual(values = c("goldenrod1","#00BFC4","blueviolet","#F8766D")) + 
  theme(legend.title=element_blank(), axis.title.x = element_text(size = font), 
        axis.title.y = element_text(size = font), legend.text = element_text(size = font) ,
        legend.position = "top",axis.text = element_text(size = font), strip.text = element_text(size = font),
        plot.margin=unit(c(1,1,0.5,0.5),"cm")) + coord_fixed(ylim = c(0,100), ratio = 0.56)


```


```{r}
# Fish bar charts
ff_pomdp_large = apply(find_pomdp_large,c(1,3),mean)
ff_pomdp_small = apply(find_pomdp_small,c(1,3),mean)
ff_pomdp_medh = apply(find_pomdp_medh,c(1,3),mean)
ff_pomdp_medl = apply(find_pomdp_medl,c(1,3),mean)
ff_mdp_large = apply(find_mdp_large,c(1,3),mean)
ff_mdp_small = apply(find_mdp_small,c(1,3),mean)
ff_mdp_medh = apply(find_mdp_medh,c(1,3),mean)
ff_mdp_medl = apply(find_mdp_medl,c(1,3),mean)
ff_msy_large = apply(find_msy_large,c(1,3),mean)
ff_msy_small = apply(find_msy_small,c(1,3),mean)
ff_msy_medh = apply(find_msy_medh,c(1,3),mean)
ff_msy_medl = apply(find_msy_medl,c(1,3),mean)


Flounder = c(7  , 8  , 9 ,107)
Tuna = c(2 , 3 , 4, 10, 11, 14 ,15, 64, 86, 88)
Mackerel = c(12 ,26 ,27, 28, 35 ,48, 53)
Rock = c(33 , 34 , 38 , 56 , 57,  79 , 80, 106)
Cod = c(29 ,30 ,31, 69 ,70)
Sole = c(37  ,39 , 58 , 76, 109)
Hake = c(25 ,36 , 46 , 72 ,93 ,100)
Oreo = c(17, 18, 89 ,90 ,91)
Anchovy = c(51, 52)
Plaice = c(5 , 6 ,73)
Herring = c(47 ,82)
Pollock = c(74 ,102 ,103 ,104 ,105)
Haddock = c(43 ,44 ,45)
Ling = c(59, 60 ,61, 62)
Whiting = c(87)
Crab = c(92, 97)
Other = c(66  ,67 , 83,  20 , 78 , 95 , 96 , 22  ,23 , 24  ,77 , 94 ,101  ,54 ,108 , 32,  84 , 85 ,
          1 ,  6 ,  9 , 38 , 10  ,14  ,16,  53 , 17  ,26,  60,  34 , 40,  44)


fish = c("Flounder","Tuna","Mackerel","Rockfish","Cod","Hake","Oreo","Anchovy","Plaice",
         "Herring","Pollock","Crab","Haddock","Whiting","Other")


model = c("ORM","SDP","MSY")

fish_data = expand.grid(fish,model)

min_fish = array(0, dim = dim(fish_data)[1])

fish2 = c("Flounder","Tuna","Mackerel","Rock","Cod","Hake","Oreo","Anchovy","Plaice",
         "Herring","Pollock","Crab","Haddock","Whiting","Other")


for(i in 1:length(fish2)){
  
  xx=  eval(parse(text = fish2[i]))
  history = ind_biomass[xx,28]
  if(sum(!history) != 0){
    ind_f = xx[!history]
  } else{
    ind_f = xx[history]
  }
  

  min_fish[fish_data$Var1 == fish[i] & fish_data$Var2 == "SDP"] = mean(ff_mdp_medh[ind_f,50]) * 100

  min_fish[fish_data$Var1 == fish[i] & fish_data$Var2 == "ORM"] = mean(ff_pomdp_medh[ind_f,50]) * 100

  min_fish[fish_data$Var1 == fish[i] & fish_data$Var2 == "MSY"] = mean(ff_msy_medh[ind_f,50]) * 100
}
fish_data= data.frame(fish_data,min_fish)


fish_data %>% ggplot() + 
  geom_hline(yintercept = 0, alpha = 0.9, size = 1.5) +
  geom_hline(yintercept = 25, alpha = 0.9, size = 1.5) +
  geom_hline(yintercept = 50, alpha = 0.9, size = 1.5) +
  geom_hline(yintercept = 75, alpha = 0.9, size = 1.5) +
  geom_hline(yintercept = 100, alpha = 0.9, size = 1.5) +
  geom_col(aes(Var1,min_fish, col = Var2, fill = Var2), width = 0.5, position=position_dodge(0.75)) +
  scale_color_manual(values = c("#00BFC4","goldenrod1","#F8766D")) + 
  scale_fill_manual(values = c("#00BFC4","goldenrod1","#F8766D")) +
  theme_bw(base_size = 30) + coord_fixed(ylim = c(0,100), ratio = .07) + 
  ylab(expression(paste("% of stock recovered above 80% ", B, "/", B[MSY]))) +
  theme(legend.title = element_blank(), axis.title.x = element_blank(),
        legend.position = "top",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),
        panel.background = element_blank(),panel.border = element_rect(size = 1),plot.background = element_rect(fill = "transparent",colour = NA)) +
  geom_vline(xintercept=seq(1.5, length(unique(fish_data$Var1))-0.5, 1), 
             lwd=.5, colour="grey", linetype = "dashed") + scale_y_discrete(expand = c(0, 0)) 






```
}